---
title: "UN Report"
author: "Courtney R Armour"
date: "1/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages,include = FALSE}
library(tidyverse)
```
 
# Introduction 

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r data, include = FALSE}
gapminder_1997 <- read_csv("../data/gapminder_1997.csv")
```

# My Plot 

```{r, echo = FALSE}
ggplot(data = gapminder_1997) + 
  aes(x = gdpPercap, y = lifeExp, color=continent, size=pop/1000000) +
  geom_point() +
  labs(x = "GDP Per Capita", y = "Life Expectancy",
       title= "Do people in wealthy countries live longer?", size="Population (in millions)")
```

```{r, include=FALSE}

  nCountries <- length(unique(gapminder_1997$country)) 

```

The number of countries that entered the above analysis was `r nCountries`. 